The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-17 paper/Analisis.tex
More on discussion

>>>>

An other interesting sample of LAEs was presented by (Yamada.T el al)
for 91 LAEs at $z=3.1$. From that sample 31 LAEs ($\sim 33 \%$) present 
a single peak profile, if this single peak is present an asymmetry it 
can be explained with the outflow model (Verhamme) due to the fact that 
we don't find any asymmetry due to rotation in  both homogeneous and central
models, while in the off-center model... But if it is not the 
case (put LAEs name for those that do not present asymmetry) now they can
be understanding with rotation.
